### 2010-07-08 trunk/latex/dissertacao/abstract.tex
versao final enviada para meus orientadores.

This work presents three dependency models in order to support the evaluation of reverse engineering tools via controlled simulations. An evaluation of the models showed that, with an appropriate choice of parameters, they produce dependency networks that are structurally similar to dependencies extracted from real software systems. This work also presents a proof of concept, demonstrating the feasibility of using one of the models to evaluate algorithms used in the context of software architecture recovery, a branch of reverse engineering.

>>>>

This paper presents computer models that generate representations which can be interpreted as dependencies between source code entities. One of the models, called BCR +, was developed in the context of this work. We have also developed a classification model that can tell, with accuracy of 96\%, whether a representation of dependencies is realistic --- that is, if it resembles representations extracted from real systems. Then, we identified parameter settings for three computational models (among them, BCR+) that favor the generation of realistic representations of dependencies.

% This work presents three dependency models in order to support the evaluation of reverse engineering tools via controlled simulations. One of them, called BCR+, was developed in the context of this work. An evaluation of the models showed that, with an appropriate choice of parameters, they produce dependency networks that are structurally similar to dependencies extracted from real software systems. Moreover, classification rules were derived to predict, with 75\% accuracy, whether a network that was generated with certain parameter values will be similar to networks extracted from software systems.

This work also presents a proof of concept, demonstrating the feasibility of using BCR+ to evaluate algorithms used in the context of software architecture recovery, a branch of reverse engineering.
